---
title: "Group 34 CA pollution burden"
author: "Conner Jainese, Max Settineri"
date: "11/16/2021"
output: html_document
---

### Setup
```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

#Attach packages
library(tidyverse)
library(janitor)
library(here)

```

### Read In The Data
```{r}
#Use read_csv() to read in data
ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()

```

### Visualizing the data
```{r}
# using gglot and geom_point to create a 2D hexbin plot of % white by EJ score
ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score)) +
  labs(y = "CES 3.0 Score", 
       x = "Percent White") +
  geom_hex() +
  scale_fill_gradient(low = "lemonchiffon", high = "darkgoldenrod4") +
  theme_minimal()
```

**Figure 1.** 2D hexbin plot of CalEnviroScreen 3.0 Indicator Scores for census tracts relative to the white percentage of the population in those tracts.  

Figure 1 indicates that census tracts with a smaller percentage of white residents tend to have higher CES 3.0 scores, indicating that these communities bear a higher pollution burden than census tracts with a larger percentage of white residents. 

### Data Citation

California Office of Environmental Health Hazard Assessment. (2018). "CalEnviroScreen 3.0." California Environmental Protection Agency.